---
title: "Cleaning steps for playstore import"
author: "ourbanow"
date: "6/26/2020"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE,          # don't show code
  warning = FALSE,       # don't show warnings
  message = FALSE,       # don't show messages (less serious warnings)
  cache = FALSE,         # set to TRUE to save results from last compilation
  eval = FALSE,
  fig.align = "center",  # center figures
  fig.height=4,          # set default figure size
  fig.width=6
)
library(magrittr)           # load libraries you always use here

```
## Executive summary

This document summarizes the steps to be taken to download the reviews from the Google play store.  
So it seems nearly impossible to perform a proper scraping with R.  
However, there is a [python package](https://github.com/JoMingyu/google-play-scraper) made for this. It works, but it returns a table which is unfortunately not properly formatted. This document will describe the cleaning steps as well.  
This document is not meant to be knited (it won't work).  

## Retrieving the data 
It must be done in Python.  
Run the command line in windows as an administrator.  First make sure the scraper package is up to date.  
`pip install google-play-scraper --upgrade`  
The formatting of the reviews changes all the time, thus this is a necessary step.  

Run the scraper as described in the github description. At best, save the file for reuse.  

Copy the produced result in Notepad++, save it as a .json file. This will color-code the code.  
Now the cleaning can begin.  

Here are the steps to be taken *manually in the notepad with the replace function*  
`replace all ' with ""`  
`replace all datetime.datetime with "datetime.datetime`  
`replace all ), " with )", "`  
`replace all )}  with )"}`  
`replace all None with "None"`  
The code should start "getting colors"  
Then, line by line replace `" with \"` where there are quotes in the text  
One all this is done, save the file, it can be loaded into R.  

Command line in R to load the file:  
```{r}
library(jsonlite)
reviews <- fromJSON(txt = "filename.json")
```